Degrees Draft Syllabus

### 2023-04-07 Bookdown Syllabus/Bookdown Syllabus.Rmd
adding photo, details about R installation, contact information

@@

@@

Perform the following series of steps

>>>>

## Contact

Feel free to email me at any time at regg19970@gmail.com.

@@

![Reggie Gilliard](./Introduction/instructor.jpg) <br/>

@@

To install R you will need about 500mb of free space on your computer (you may actually need less, but freeing up 500 mb ensures you will be able to download the data and packages used in the course). Perform the following series of steps:
